Insert the article title here

### 2018-04-20 writeup/manuscript.tex
A little more intro

Another example of differences in search strategy comes from the foraging literature \cite{kristjansson2014,johannesson2016}.

>>>>

Another example of differences in search strategy comes from the foraging literature \cite{kristjansson2014,johannesson2016}. Participants were asked to search through a set of items from four categories, two of which were classed as targets. In the conjunction condition (i.e. searching for red-horizontal and green-vertical line segments among red-vertical and green-horizontal distracters), most observers searched in runs of one target or another. This strategy has previously been observers in animal foraging literature \ldots. However, a sub-set of observers, termed ``super-searchers'' showed no switch cost.
